\Title

### 2016-03-23 manuscript/manuscript.tex
Minor change to sentence in CV section
Corrections to Moho model for SAm by Val

\begin{abstract}
    Estimating the relief of the Moho from gravity data is a computationally
    intensive non-linear inverse problem.
    What is more, the modeling must take the Earths curvature into account when
    the study area is of regional scale or greater.
    We present a regularized non-linear gravity inversion method that has a low
    computational footprint and employs a spherical Earth approximation.
    To achieve this, we combine the highly efficient Bott's method with
    smoothness regularization and a discretization of the anomalous Moho into
    tesseroids (spherical prisms).
    The computational efficiency of our method is attained by harnessing the
    fact that all matrices involved are sparse.
    The inversion results are controlled by three hyper-parameters: the
    regularization parameter, the anomalous Moho density-contrast, and the
    reference Moho depth.
    We estimate the regularization parameter using the method of hold-out
    cross-validation.
    Additionally, we estimate the density-contrast and the reference depth
    using knowledge of the Moho depth at certain points.
    We apply the proposed method to estimate the Moho depth for the South
    American continent using satellite gravity data and seismological data.
    The final Moho model is in accordance with previous gravity-derived models
    and seismological data.
    The misfit to the gravity and seismological data is worse in the Andes and
    best in oceanic areas, central Brazil and Patagonia, and along the Atlantic
    coast.
    Similarly to previous results, the model suggests a thinner crust of 30-35
    km under the Andean foreland basins.
    Discrepancies with the seismological data are greatest in the Guiana
    shield, the central Solimões and Amazon Basins, the Paraná Basin, and the
    Borborema province.
    These differences suggest the existence of crustal or mantle density
    anomalies that were unaccounted for during gravity data processing.
\end{abstract}

@@

We estimate these hyper-parameters in two steps.
First, we assume fixed values for
$z_{ref}$ and $\Delta\rho$ and perform a cross-validation procedure
\citep{hansen1992} to estimate an optimal value for $\mu$.
Our investigations suggest that the outcome of this round of cross-validation
does not depend on the particular values of $z_{ref}$ and $\Delta\rho$ used.
Second, we use the estimated $\mu$ to perform a second cross-validation
procedure to estimate $z_{ref}$ and $\Delta\rho$.
The outcome of both cross-validations is not only the values of the three
hyper-parameters but the final estimated Moho depths.

@@

The final Moho depth model for South America is shown
as a pseudo-color map in Fig.~\ref{fig:sam-moho}a.
The model is available in the online repository that accompanies
this contribution (see section~\ref{sec:software}).
Each model element is a $0.4^\circ \times 0.4^\circ$ tesseroid,
represented by the pixels in the pseudo-color map.

Our model differs significantly from CRUST1.0 (Fig.~\ref{fig:crust1-data}a)
but contains most of the large-scale features
present in the GMSA12 gravity-derived model of \citet{vandermeijde2013}.
The deepest Moho is along the central Andes, reaching depths upward of 70 km.
The oceanic areas present the shallowest Moho, ranging approximately
from 7.5 to 20 km.
The Brazilian and Guiana shields have a deeper Moho (greater than 35 km),
with the deepest portion in the area of the São Francisco craton.
The Moho is shallower than 35 km along the western Amazon and Andean foreland
regions, as well as along the Amazon river.

Fig.~\ref{fig:sam-moho}b shows the inversion residuals
(observed minus predicted data)
and Fig.~\ref{fig:sam-moho}c shows the differences between
the seismic-derived depths of \citet{assumpcao2013a}
(Fig.~\ref{fig:sam-data}b) and the depths in our model.
The differences range from approximately -23 to 23 km
and have a mean of 1.18 km and a standard deviation of 6.84 km.
The residuals and differences from seismic are smallest in the oceanic areas,
southern Patagonia, and the eastern coast of the continent.
The largest residuals are located along the Andes and correlate with the
deepest Moho depths.
These large residuals follow a pattern of a negative value in the center
flanked by positive values to the East and West.
This same pattern is observed in the CRUST1.0 synthetic test results
(Fig.~\ref{fig:crust1-results}),
suggesting that this is a byproduct of the inversion method, not the data.
Likewise, larger residuals also appear to be associated with sharp variations
in the estimated Moho depth.
Along the Andes, large differences with seismic data are correlated with the
large inversion residuals.
Conversely, this correlation is absent from the large differences seen in
points around Venezuela.
In the Borborema province, northeastern Brazil,
our model slightly overestimates the Moho depth.
On the other hand, our model underestimates the depths
in the Amazon region and the Paraná Basin.
Particularly in the Amazon Basin,
where our model predicts a Moho depth of approximately 30 km,
the residuals and the differences with the seismic data are larger than in the
Paraná Basin.

@@

We applied the method proposed here to estimate the Moho depth for South
America.
Our estimated Moho depth model is in accordance with previous results by
\citet{vandermeijde2013}.
The model fits well the gravity and seismic data in all oceanic regions, the
central portion of the Andean foreland, Patagonia, and coastal and central
parts of Brazil.
However, the model is unable to fit the gravity and seismic data in places with
sharp variations in Moho depth, particularly below the Andes and in the
boundaries of the main geotectonic provinces of the South American Plate, like
the Borborema province, the Parnaiba Basin, and the São Francisco Craton.
This might indicate that smoothness regularization should not be applied
indiscriminately to the whole model, as suggested by the CRUST1.0 synthetic
data test.
Another reason for the observed misfit might be the presence of crustal or
mantle density anomalies whose gravitational effects were not removed during
the data corrections.
In the coastal region of Venezuela, along the central Amazon and Solimões
Basins, and in the Paraná Basin, our Moho depth model is able to fit the
gravity data but differs significantly from the seismic data.
\citet{mariani2013} and \citet{nunn1988} explain these discrepancies in the
Paraná and Amazon Basins, respectively, as high density rocks in the lower
crust.
In general, differences between a gravity and a seismically derived Moho model
may indicate the presence of crustal or mantle density anomalies that were
unaccounted for in the data processing.
Such locations warrant further detailed investigation.

>>>>

\begin{abstract}
    Estimating the relief of the Moho from gravity data is a computationally
    intensive non-linear inverse problem.
    What is more, the modeling must take the Earths curvature into account when
    the study area is of regional scale or greater.
    We present a regularized non-linear gravity inversion method that has a low
    computational footprint and employs a spherical Earth approximation.
    To achieve this, we combine the highly efficient Bott's method with
    smoothness regularization and a discretization of the anomalous Moho into
    tesseroids (spherical prisms).
    The computational efficiency of our method is attained by harnessing the
    fact that all matrices involved are sparse.
    The inversion results are controlled by three hyper-parameters: the
    regularization parameter, the anomalous Moho density-contrast, and the
    reference Moho depth.
    We estimate the regularization parameter using the method of hold-out
    cross-validation.
    Additionally, we estimate the density-contrast and the reference depth
    using knowledge of the Moho depth at certain points.
    We apply the proposed method to estimate the Moho depth for the South
    American continent using satellite gravity data and seismological data.
    The final Moho model is in accordance with previous gravity-derived models
    and seismological data.
    The misfit to the gravity and seismological data is worse in the Andes and
    best in oceanic areas, central Brazil and Patagonia, and along the Atlantic
    coast.
    Similarly to previous results, the model suggests a thinner crust of 30-35
    km under the Andean foreland basins.
    Discrepancies with the seismological data are greatest in the Guyana
    Shield, the central Solimões and Amazonas Basins, the Paraná Basin, and the
    Borborema province.
    These differences suggest the existence of crustal or mantle density
    anomalies that were unaccounted for during gravity data processing.
\end{abstract}

@@

We estimate these hyper-parameters in two steps.
First, we assume fixed values for
$z_{ref}$ and $\Delta\rho$ and perform a cross-validation procedure
\citep{hansen1992} to estimate an optimal value for $\mu$.
Our investigations suggest that the optimal value of $\mu$ does not depend on
the particular values of $z_{ref}$ and $\Delta\rho$ used.
Second, we use the estimated $\mu$ to perform a second cross-validation
procedure to estimate $z_{ref}$ and $\Delta\rho$.
The outcome of both cross-validations is not only the values of the three
hyper-parameters but the final estimated Moho depths.

@@

The final Moho depth model for South America is shown
as a pseudo-color map in Fig.~\ref{fig:sam-moho}.
The model is available in the online repository that accompanies
this contribution (see section~\ref{sec:software}).
Each model element is a $0.4^\circ \times 0.4^\circ$ tesseroid,
represented by the pixels in the pseudo-color map.

Our model differs significantly from CRUST1.0 (Fig.~\ref{fig:crust1-data}a)
but contains most of the large-scale features
present in the GMSA12 gravity-derived model of \citet{vandermeijde2013}.
The deepest Moho is along the central Andes, reaching depths upward of 70 km.
The oceanic areas present the shallowest Moho, ranging approximately
from 7.5 to 20 km.
The Brazilian and Guyana Shields have a deeper Moho (greater than 35 km),
with the deepest portions in the area around the São Francisco Craton
and the northern border of the Parecis Basin.
The Moho is shallower than 35 km along the Guyana Basin, the Andean foreland
basins, the Chaco Basin, and along the centers of the Solimões, Amazonas, and
Paraná Basins.

Fig.~\ref{fig:sam-residuals}a shows the gravity residuals,
defined as the difference between the observed and predicted gravity data.
Fig.~\ref{fig:sam-residuals}b shows the differences between
the seismic-derived Moho depths of \citet{assumpcao2013a}
(Fig.~\ref{fig:sam-data}b) and the depths of our gravity-derived model
(Fig.~\ref{fig:sam-moho}).
The differences shown in Fig.~\ref{fig:sam-residuals}b range from approximately
-23 to 23 km and have a mean of 1.18 km and a standard deviation of 6.84 km.
The gravity residuals and Moho depth differences from seismic are smallest in
the oceanic areas, southern Patagonia, and the eastern coast of the continent.
The largest gravity residuals are located along the Andes and correlate with
the deepest Moho depths.
These large residuals follow a pattern of a negative value in the center
flanked by positive values to the east and west.
This same pattern is observed in the CRUST1.0 synthetic test results
(Fig.~\ref{fig:crust1-results}).
In general, larger gravity residuals appear to be associated with sharp
variations in the estimated Moho depth.
Along the Andes, large differences with seismic data are correlated with the
larger gravity residuals.
Conversely, this correlation is absent from the large differences seen in the
Guyana, Paraná, and the Solimões Basins.
In the Borborema province, northeastern Brazil,
our model slightly overestimates the Moho depth.
On the other hand, our model underestimates the Moho depths in the Amazonas,
Solimões, and Paraná Basins.
Particularly in the Amazonas and Solimões Basins, where our model predicts a
Moho depth of approximately 30 km, the differences with the seismological
estimates can reach 10 km or more.

@@

We applied the method proposed here to estimate the Moho depth for South
America.
Our estimated Moho depth model is in accordance with previous results by
\citet{vandermeijde2013}.
The model fits well the gravity and seismic data in all oceanic regions, the
central portion of the Andean foreland, Patagonia, and coastal and central
parts of Brazil.
However, the model is unable to fit the gravity and seismic data in places with
sharp variations in Moho depth, particularly below the Andes and in the
boundaries of the main geotectonic provinces of the South American Plate, like
the Borborema province, the Parnaiba Basin, and the São Francisco Craton.
This might indicate that smoothness regularization should not be applied
indiscriminately to the whole model, as suggested by the CRUST1.0 synthetic
data test.
Another reason for the observed misfit might be the presence of crustal or
mantle density anomalies whose gravitational effects were not removed during
the data corrections.
In the Guyana Basin on the coastal region of Venezuela, along the central
Amazonas and Solimões Basins, and in the Paraná Basin, our Moho depth model is
able to fit the gravity data but differs significantly from the seismic data.
\citet{mariani2013} and \citet{nunn1988} explain these discrepancies in the
Paraná and Amazonas Basins, respectively, as high density rocks in the lower
crust.
In general, differences between a gravity and a seismically derived Moho model
may indicate the presence of crustal or mantle density anomalies that were
unaccounted for in the data processing.
Such locations warrant further detailed investigation.
